---
title: "Traffic Modeling"
author: "Michael DeAmico and Collaborators"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["chapters/references.bib"]
biblio-style: "apalike"
link-citations: true
---
# Preface {-}

This website provides a collection of thoughts on traffic modeling, specifically the practical application of microsimulation.
The intent is to:

- Provide a concise source of practical knowledge
- Inspire collaboration between traffic engineers
- Encourage better transportation decision making

Existing guidance on traffic microsimulation has traditionally been passed down by word of mouth or found within state or federal guidance that have slow update cycles.
This website is a living document, with all updates and discussions open for the community to see. 

# License {- #license}

```{r child='./_LICENSE.Rmd'}
```

# Disclaimer {- #disclaimer}

```{r child='./_disclaimer.Rmd'}
```

# Contribute {-}

Anyone can submit ideas, content, and revisions to this website.
You do not need to know anything about website development, but you will need to learn a few concepts related to Github which provides the website hosting and issue tracking features.

 - Anyone contributing must follow the [Code of Conduct](#code-of-conduct)
 - Anyone contributing agrees to the [license](#license)

```{r child='./_CONTRIBUTING.Rmd'}
```

